The shape of dark matter halos in the AURIGA simulations

### 2019-07-10 Document/paper.tex
new plots

  \subfloat[MHD shape at small radius]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_2.png}} 
  \hfill
  \subfloat[MHD shape at large radius]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_4.png}} 
  \hfill 
  \caption{DM density in a slice with width one tenth of the virial radius.
  The black ellipses show the result of the fitting procedure. 
  Upper panels correspond to DM only simulations, lower panels to MHD simulations.
  Left panels show data at small radii, while right panels at large radii.}
\label{fig:slices}
\end{figure*}

@@

We restrict the sampling of the ellipsoidal parameters to radii
between $1/16 R_{vir}$ and $2R_{vir}$, where  $R_{vir}$ is taken as the
radius enclosing a sphere with 500 times the average dark matter
density of the Universe. 
All our results use of this reference radius
unless strictly stated otherwise. 
We peform the shape measurements both as a function of radius and
redshift for all halos in the sample.

@@

\begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/MHD_Vs_DM/halo16_new.png}}
\caption{Radial profile for the axial ratios and the triaxiality parameter
  $T=\frac{1-b/a}{1-c/a}$ at redshift $z=0$. 
  Radial profile was sampled at
  redshift 0 and there are two sets of lines showing MHD and DM-only
  versions of the axial ratios profile. {\bf Aqui hay que quiar c/b,
    no es relevante}} \label{fig:triaxial_radius}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_DM.png}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_MHD.png}
\end{center}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
  on the left and MHD simulations on the right.
   Each dot represents the shape characterization of each halo at the virial radius and a  1/8 fraction of the virial radius
   differentiated by color. 
   Errorbar shows median and errors for each sampled radii. 
   Conclusion: DM halos are rounder on the outskirts {\bf Esto necesita
  correccion. Debe ser a R1/16 y R (no 2R!) Corregido!}}
  \label{fig:triax_DM_MHD}
\end{figure*}

@@

{\bf Hace falta una grafica de la distribucion cumulativa de
  triaxialidad para (R\_vir y R\_vir/16 por separado), en cada panel se
  com para MHD vs DM.}

  \begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/Star_Disk_Alignment/Cummulative_Alignment_Histogram_Rvir.png}}
\caption{Cummulative distribution of alignment $cos\theta$ between the minor axis vector sampled as R virial and the star disk vector} \label{fig:alignment_out}
\end{figure*}

  \begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/Star_Disk_Alignment/Cummulative_Alignment_Histogram_Rvir_16.png}}
\caption{Cummulative distribution of alignment $cos\theta$ between the minor axis vector sampled as 1/16 of R virial and the star disk vector} \label{fig:alignment_in}
\end{figure*}

@@

  \begin{table}
\setlength{\tabcolsep}{3pt}
\begin{center}
\begin{tabular}{l|ccc}
 Variable/Method& Lasso& Random Forest & MCMC \\
 & (slope) & (feature importance)&(signal-to noise)\\
\hline 
Star disk Radius &$-0.168 (1)$&$23\% (2)$&$-0.140$  (3)\\[0.1cm]
Gas Radius&$0.081 (5)$&$12.6\% (5)$&$0.217 (1)$\\[0.1cm] 
Star Density &$-0.064 (6)$&$15.2\% (4)$&$-0.102 (6)$\\[0.1cm]
BH Density&$0.084 (4)$&$16.1\% (3)$&$0.108 (5)$\\[0.1cm] 
Gas Density &$0.097 (3)$&$28.4 \%(1)$&$0.202 (2)$\\[0.1cm] 
Baryonic fraction &$-0.167 (2)$&$4\% (6)$&$/0.146 (4)$\\[0.1cm]  
\end{tabular}
\end{center}
\caption{Results of variable importance of the three methods used to analyse
		 the effect of baryons on the rounding effect of halos. Each method has a different
		 metric for the variable importance and are not comparable but in rankings}  
\label{table:sphericity}
\end{table} 
  \begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/Sphericity/Sphericity_signal_to_noise.png}}
\caption{Distribution of likelihood for different values of the linear parameters. This gives us an idea of the consistency of the fit } \label{fig:sphericity}
\end{figure*}

>>>>

  \subfloat[MHD shape at small radius]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_2.png}} 
  \hfill
  \subfloat[MHD shape at large radius]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_4.png}} 
  \hfill 
  \caption{DM density in a slice with width one tenth of the virial radius.
  The black ellipses show the result of the fitting procedure. 
  Upper panels correspond to DM only simulations, lower panels to MHD simulations.
  Left panels show data at small radii, while right panels at large
  radii.
  The cut is made along the minor axis of the halo shape.}
\label{fig:slices}
\end{figure*}

\begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/MHD_Vs_DM/halo16_new.png}}
\caption{Radial profile for the axial ratios $b/a$, $c/a$, and the triaxiality parameter
  $T$ at redshift $z=0$.
  The continous/dashed lines correspond to the MHD/DM simulations respectively.
  The vertical line corresponds to the virial radius.}
\label{fig:triaxial_radius}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_DM.png}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_MHD.png}
\end{center}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
  on the left and MHD simulations on the right.
   Each dot represents the shape characterization of each halo 
   Red circles represent measurements at the virial radius and the
   blue squares are measurements at 1/8 of the virial radius.   
   The crosses represent the mean values and standard deviation of
   each sample.
   Overall we can see three things. 
   First, in DM only simulations halos are rounder in the outskirts
   than in the inner part.
   Second, halos in MHD are rounder than its DM only counterparts.
   Third, halos in MHD simulations are slightly rounder in the inner
   part compared to the outskirts.}
  \label{fig:triax_DM_MHD}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_DM.pdf}
\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_MHD.pdf}
\caption{Cumulative fraction of the triaxiality for all 30 halos in
  Level 4 simulations. Right/left panel correspond to DM/MHD
  simulations respectively. 
  This quantifies the main trends we find: in DM only simulations
  rounder in the outskirts, halos in MHD are rounder than DM only, and
  in MHD simulations halos tend to be rounder at the inner regions
  than its outskirts.}
\label{fig:triax_cumulative}
\end{figure*}

\begin{figure}
\includegraphics[width=0.9\columnwidth]{delta_triaxialiy_distro.pdf}
\caption{Cumulative fraction of the changes in the triaxility betwen
  MHD and DM simulations at different radii. 
  At all radii at least $80\%$ of the halos became rounder in the MHD
  simulations. 
  However, the effect is more pronounced at smaller radii.}
\label{fig:triax_difference}
\end{figure}

@@

We restrict the sampling of the ellipsoidal parameters to radii
between $1/16 R_{vir}$ and $2R_{vir}$, where  $R_{vir}$ is taken as the
radius enclosing a sphere with 200 times the average dark matter
density of the Universe. 
All our results use of this reference radius
unless strictly stated otherwise. 
We peform the shape measurements both as a function of radius and
redshift for all halos in the sample.

@@

@@

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{cumulative_alignment.pdf}
\caption{Cumulative distribution of alignment $\cos\theta$ between the
  minor axis of the dark matter halo at different radii and the
  stellar disk.} \label{fig:alignment_out}
\end{figure}

@@

  \begin{table}
\setlength{\tabcolsep}{3pt}
\begin{center}
\begin{tabular}{l|ccc}
 Variable/Method& Lasso& Random Forest & MCMC \\
 & (slope) & (feature importance)&(signal-to noise)\\
\hline 
Star disk Radius &$-0.168 (1)$&$23\% (2)$&$-0.140$  (3)\\[0.1cm]
Gas Radius&$0.081 (5)$&$12.6\% (5)$&$0.217 (1)$\\[0.1cm] 
Star Density &$-0.064 (6)$&$15.2\% (4)$&$-0.102 (6)$\\[0.1cm]
BH Density&$0.084 (4)$&$16.1\% (3)$&$0.108 (5)$\\[0.1cm] 
Gas Density &$0.097 (3)$&$28.4 \%(1)$&$0.202 (2)$\\[0.1cm] 
Baryonic fraction &$-0.167 (2)$&$4\% (6)$&$/0.146 (4)$\\[0.1cm]  
\end{tabular}
\end{center}
\caption{Results of variable importance of the three methods used to analyse
		 the effect of baryons on the rounding effect of halos. Each method has a different
		 metric for the variable importance and are not comparable but in rankings}  
\label{table:sphericity}
\end{table}

%  \begin{figure*}
%\centering
%{\includegraphics[width=0.6\textwidth]{./pics/Sphericity/Sphericity_signal_to_noise.png}}
%\caption{Distribution of likelihood for different values of the linear parameters. This gives us an idea% of the consistency of the fit } \label{fig:sphericity}
%\end{figure*}
